Fitbit & ET Glasses - Methods

### 2022-09-30 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
fitbit anova
upload fitbit data

keywords          : "heart rate; photoplethysmography; wearable electronic device; expertise differences "
wordcount         : "X"

@@

needs(tidyverse,
      lubridate,
      janitor,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable)

@@

# read in data and select and rename relevant columns with transmute 
demo.data <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  transmute(Group = LI06_05,
            Gender = LI02_01_1,
            Age = LI03_01,
            `Teaching Experience` = LI04_01,
            School_type = LI18,
            Grade = LI16_05,
            Subject = LI10_05,
            Semester = LI11_01,
            Internship = LI13_01,
            `Extracurricular Teaching Experience` = LI14,
            `Secondary Teaching Activities` = LI17
            )

# define expert and novice with ifelse function
demo.data$Group = ifelse(demo.data$Group < 200, "Novice","Expert")

@@

# creating new column with total participants to calculate percent of gender
demo.data <- demo.data %>%
  group_by(Group) %>%
  mutate(Sum_participants = n())

@@

# creating new column to calculate percent of school type
demo.data <- 
  demo.data %>%
  group_by(School_type, Group) %>%
  mutate(Count_Schooltype = sum(n())) %>% 
  mutate(Percent_schooltype = round((Count_Schooltype/Sum_participants) * 100, 
         digits = 2))

@@

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female in percent" = round(sum(Gender/Sum_participants) * 100, 
                                               digits = 2),
            "M Age in years" = round(mean(Age), 
                                     digits = 2),
            "SD Age in years" = round(sd(Age), 
                                      digits = 2),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age)
            )

@@

# create a basic table (tibble) using tidyverse functions
exp.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
           "M Exp." = round(mean(`Teaching Experience`), 2),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "M Semester" = round(mean(Semester), 2),
            "SD Semester" = round(sd(Semester), 2),
            "Min Semester" = min(Semester),
            "Max Semester" = max(Semester),
            "M Internship" = round(mean(Internship), 2),
            "SD Internship" = round(sd(Internship), 2),
            "Min Internship" = min(Internship),
            "Max Internship" = max(Internship),
            "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
            "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
           )

@@

XXX  fitbit data exclusion XXX

The sample consisted of *N* = `r length(demo.data$Group)` participants with *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` expert teachers and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novice teachers.

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`). 
`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers. `r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years. On average, the student teachers were in their `r exp.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`). Furthermore, they had an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Internship")`) through the internships during their studies. 
`r demo.data %>% filter(Group == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(Group == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% to become secondary school teachers and `r demo.data %>% filter(Group == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype") %>% unique()`% to become special education teachers. `r exp.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

XXX Data and data wrangling need to be imported XXX 
```{r}
# # Initial Preparations
# ## Run following Code if and only if new data is added to the initial data.
# 
# source(file = "data.wrangling.R")
# 
# 
# # Plots
# 
# df_heart_all <-
#   read_rds(file = "final_data/heart_all.rds") |> 
#   mutate(status = factor(status,
#                          levels = c("Expert","Novice"),
#                          labels = c("Expert","Novice")
#                          )
#          )
# 
# df_heart_min <-
#   read_rds(file = "final_data/heart_min.rds")
# 
# df_heart_aggr <- 
#   read_rds(file = "final_data/heart_aggr.rds") |> 
#   mutate(status = factor(status,
#                          levels = c("Novice","Expert"),
#                          labels = c("Novice","Expert")
#                          )
#          )
# 
# plot_flow <-
# ggplot(data = df_heart_all,
#        mapping = aes(x = as.numeric(Time),
#                      y = `Heart Rate`,
#                      group = ID)
#        ) +
#   geom_line(mapping = aes(color = status),
#             size = 0.3,
#             alpha = 1
#             ) +
#   xlim(0, min(df_heart_min$min)) +
#   scale_color_viridis_d(option = "A",
#                        end = 0.8)  +
#   scale_linetype_manual(values = c(1, 6)) +
#   labs(x = "Time (in Seconds)",
#        y = "Heart Rate\n(in Beats per Minute)") +
#   theme_minimal() +
#   theme(text = element_text(family = "serif"),
#         legend.position = "none",
#         strip.text = element_text(size = 16)) +
#   facet_grid(cols = vars(Type),
#              scales = "free_x")
# 
# plot_flow_leg <-
# ggplot(data = df_heart_all,
#        mapping = aes(x = Time,
#                      y = `Heart Rate`
#                      )
#        ) +
#   geom_smooth(mapping = aes(color = status),
#               method = "loess") +
#   scale_color_viridis_d(option = "A",
#                         end = 0.8) +
#  # scale_linetype_manual(values = c(1, 6)) +
#   theme_minimal() +
#   theme(text = element_text(family = "serif"),
#         legend.title = element_blank()) 
# 
# legend <- cowplot::get_legend(plot_flow_leg)
# 
# plot_loess <-
# ggplot(data = filter(df_heart_all),
#        mapping = aes(x = as.numeric(Time),
#                      y = `Heart Rate`
#                      )
#        ) +
#   stat_smooth(geom = "line",
#               mapping = aes(color = status),
#               method = "loess",
#               se = FALSE) +
#   xlim(0,min(df_heart_min$min)) +
#   scale_color_viridis_d(option = "A",
#                         end = 0.8) +
#   scale_linetype_manual(values = c(1, 6)) +
#   labs(x = "Time (in Seconds)",
#        y = "Heart Rate\n(in Beats per Minute)") +
#   theme_minimal() +
#   facet_grid(cols = vars(Type),
#              scales = "free_x",
#              ) +
#   theme(text = element_text(family = "serif"),
#         legend.position = "none",
#         strip.background = element_blank(),
#         strip.text.x = element_blank()
#         )
# 
# plot_box <- 
# ggplot(data = df_heart_aggr,
#        mapping = aes(x = Type,
#                      y = mean,
#                      color = status
#                      )
#        ) +
#   geom_boxplot(color = "darkgrey",
#                fill = "grey") +
#   geom_line(data = filter(df_heart_aggr,
#                           status == "Novice"),
#             mapping = aes(x = Type,
#                           y = mean,
#                           group = as_factor(ID)
#                           ),
#             linetype = 1,
#             alpha = 0.5
#             ) +
#   geom_line(data = filter(df_heart_aggr,
#                           status == "Expert"),
#             mapping = aes(x = Type,
#                           y = mean,
#                           group = as_factor(ID)
#                           ),
#             linetype = 6,
#             alpha = 0.5
#             ) +
#   geom_point(size = 2,
#              alpha = 0.5) +
#   labs(x = "",
#        y = "Average Heart Rate\n(in Beats per Minute)") +
#   scale_color_viridis_d(option = "A",
#                        end = 0.8) +
#   theme_minimal() +
#   theme(text = element_text(family = "serif"),
#         strip.text = element_blank(),
#        legend.position = "none",
#         axis.text.x = element_blank()
#         ) +
#   aes(fill = Type)
# 
# lo_mat <- rbind(c(1,1,1,1,1,1,NA),
#                 c(2,2,2,2,2,2,4),
#                 c(3,3,3,3,3,3,NA))
# 
# plot_heart <- 
# grid.arrange(grobs = list(plot_flow, plot_loess, plot_box, legend),
#              layout_matrix = lo_mat)
# 
# plot_heart

@@

```{r}
# df_steps <- read_rds(file = "final_data/steps.rds")
# set.seed(5678)
# ggplot(data = df_steps,
#        mapping = aes(x = type,
#                      y = Steps
#                      )
#        ) +
#   geom_boxplot(mapping = aes(color = type),
#                fill = "grey",
#                alpha = 0.6) +
#   geom_jitter(mapping = aes(color = type),
#               alpha = 0.9,
#               width = 0.3) + 
#   scale_color_viridis_d(option = "A",
#                        end = 0.8) +
#   labs(x = "",
#        y = "Steps During\nMain Phase") +
#   theme_minimal() +
#   theme(text = element_text(family = "serif"),
#         legend.title = element_blank(),
#         axis.text.x = element_blank(),
#         axis.ticks.x = element_blank()
#         ) 
# 
# ### Validation of steps 
# # selecting some rows at random with sample_n()
# sample_n(df_steps, 6)
# 
# # random ID Output:
# # Novices ID: 102, 125, 110
# # Experts ID: 219, 218, 214
# 
# # Results from manual step counting:
# # Novices ID: 110 -> 178 steps; 102 -> 219 steps; 125 -> 319 steps
# # Experts ID: 214 -> 437 steps; 218 -> 195 steps; 219 -> 530 steps

>>>>

keywords          : "heart rate; photoplethysmography; wearable electronic device; expertise differences"
wordcount         : "X"

@@

needs(tidyverse,
      lubridate,
      janitor,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      ggthemes,
      imputeTS,
      rstatix,
      ggpubr)

@@

# DEMOGRAPHIC DATA
# read in data and select and rename relevant columns with transmute 
demo.data.raw <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  transmute(ID = LI06_05,
            Gender = LI02_01_1,
            Age = LI03_01,
            `Teaching Experience` = LI04_01,
            School_type = LI18,
            Grade = LI16_05,
            Subject = LI10_05,
            Semester = LI11_01,
            Internship = LI13_01,
            `Extracurricular Teaching Experience` = LI14,
            `Secondary Teaching Activities` = LI17
            )

# exclude cases with no fitbit data
demo.data.raw <- demo.data %>% filter(!ID %in% c("126",
                                                 "132"
                                                 )
                                      )

# define expert and novice with ifelse function
demo.data$ID = ifelse(demo.data$ID < 200, "Novice","Expert")

@@

# creating new column with total participants to calculate percent of gender
demo.data <- demo.data %>%
  group_by(ID) %>%
  mutate(Sum_participants = n())

@@

# creating new column to calculate percent of school type
demo.data <- 
  demo.data %>%
  group_by(School_type, ID) %>%
  mutate(Count_Schooltype = sum(n())) %>% 
  mutate(Percent_schooltype = round((Count_Schooltype/Sum_participants) * 100, 
         digits = 2))

@@

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(ID) %>%
  summarise(N=n(),
            "Gender female in percent" = round(sum(Gender/Sum_participants) * 100, 
                                               digits = 2),
            "M Age in years" = round(mean(Age), 
                                     digits = 2),
            "SD Age in years" = round(sd(Age), 
                                      digits = 2),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age)
            )

@@

# create a basic table (tibble) using tidyverse functions
exp.table <- demo.data %>%
  group_by(ID) %>%
  summarise(N=n(),
           "M Exp." = round(mean(`Teaching Experience`), 2),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "M Semester" = round(mean(Semester), 2),
            "SD Semester" = round(sd(Semester), 2),
            "Min Semester" = min(Semester),
            "Max Semester" = max(Semester),
            "M Internship" = round(mean(Internship), 2),
            "SD Internship" = round(sd(Internship), 2),
            "Min Internship" = min(Internship),
            "Max Internship" = max(Internship),
            "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
            "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
           )

@@

The sample consisted of *N* = `r length(demo.data$ID)` participants with *n* = `r length(demo.data$ID[demo.data$ID == "Expert"])` expert teachers and *n* = `r length(demo.data$ID[demo.data$ID == "Novice"])` novice teachers.

The data of two participants (two novices, XXX experts) were excluded from the analyses due to insufficient data quality.

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & ID == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(ID == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(ID == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(ID == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(ID == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(ID == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(ID == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(ID == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(ID == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(ID == "Expert") %>% pull("Max Exp.")`). 
`r demo.data %>% filter(ID == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(ID == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers. `r exp.table %>% filter(ID == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (`r demo.data %>% filter(Gender == 1 & ID == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(ID == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(ID == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(ID == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(ID == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(ID == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(ID == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years. On average, the student teachers were in their `r exp.table %>% filter(ID == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(ID == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(ID == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(ID == "Novice") %>% pull("Max Semester")`). Furthermore, they had an average teaching experience of `r exp.table %>% filter(ID == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(ID == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(ID == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(ID == "Novice") %>% pull("Max Internship")`) through the internships during their studies. 
`r demo.data %>% filter(ID == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(ID == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% to become secondary school teachers and `r demo.data %>% filter(ID == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype") %>% unique()`% to become special education teachers. `r exp.table %>% filter(ID == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

```{r}
# Initial Preparations
## Run following Code if and only if new data is added to the initial data.

source(file = "data.wrangling.R")

# Mean, SD, t-test & Cohen D for experts & novices
# novices
mean_nov <- 
  df_heart_aggr %>%
  filter(status == "Novice" ) %>% 
  pull(mean) %>% 
  mean() %>% 
  round(., digits = 0)

sd_nov <- 
  df_heart_aggr %>%
  filter(status == "Novice") %>% 
  pull(mean) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_exp <-
  df_heart_aggr %>%
  filter(status == "Expert") %>% 
  pull(mean) %>% 
  mean() %>% 
  round(., digits = 0)

sd_exp <- 
  df_heart_aggr %>%
  filter(status == "Expert") %>% 
  pull(mean) %>% 
  sd() %>% 
  round(., digits = 0)

# t-test for expertise differences
t.test(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
       y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"])

# effect size for expertise differences
d_heartrate <- CohenD(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
               y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"],
               na.rm = TRUE)

# Plots

df_heart_all <-
  read_rds(file = "data/heart_all.rds") |>
  mutate(status = factor(status,
                         levels = c("Expert","Novice"),
                         labels = c("Expert","Novice")
                         )
         )

df_heart_min <-
  read_rds(file = "data/heart_min.rds")

df_heart_aggr <-
  read_rds(file = "data/heart_aggr.rds") |>
  mutate(status = factor(status,
                         levels = c("Novice","Expert"),
                         labels = c("Novice","Expert")
                         )
         )

plot_flow_leg <-
ggplot(data = df_heart_all,
       mapping = aes(x = Time,
                     y = `Heart Rate`
                     )
       ) +
  xlim(0, 600) +
  geom_smooth(mapping = aes(color = status),
              method = "loess") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Time (in Seconds)",
       y = "Heart Rate\n(in Beats per Minute)") +
  ggtitle("Experts' and novices' heart rate per phase") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 10),
        strip.text = element_text(size = 16),
        plot.title = element_text(size = 20, 
                                  face = "bold")) +
  facet_grid(cols = vars(Type),
             scales = "free_x")

legend <- cowplot::get_legend(plot_flow_leg)

# saving plot 
ggsave(plot = plot_flow_leg,
       filename = "Plots/plot_flow_leg.svg",
       height = 5,
       width = 8,
       units = "in")

############### BOX PLOT #############

##### Box 1 Plot ##### 
plot_box1 <- 
ggplot(data = df_heart_aggr,
       mapping = aes(x = Type,
                     y = mean,
                     color = status
                     )
       ) +
  geom_boxplot(color = "darkgrey",
               fill = "grey") +
  geom_line(data = filter(df_heart_aggr,
                          status == "Novice"),
            mapping = aes(x = Type,
                          y = mean,
                          group = as_factor(ID)
                          ),
            linetype = 1,
            alpha = 0.5
            ) +
  geom_line(data = filter(df_heart_aggr,
                          status == "Expert"),
            mapping = aes(x = Type,
                          y = mean,
                          group = as_factor(ID)
                          ),
            linetype = 6,
            alpha = 0.5
            ) +
  geom_point(size = 2,
             alpha = 0.5) +
  labs(x = "",
       y = "Average Heart Rate\n(in Beats per Minute)") +
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        strip.text = element_blank(),
        legend.position = "none",
        axis.text.x = element_blank()
        ) +
  aes(fill = Type)

plot_box1

##### Box 2 Plot ##### 
plot_box <-
  ggplot(data = df_heart_aggr,
         mapping = aes(x = Type,
                       y = mean)) + 
  geom_boxplot(mapping = aes(fill = status),
               outlier.shape = NA) +
  geom_point(mapping = aes(shape = status),
             alpha = 0.5,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  labs(x ="",
       y = "Average Heart Rate\n(in Beats per Minute)") + 
  ggtitle("Experts' and novices' heart rate per phase") +
  scale_fill_brewer(palette  = "RdBu") +  
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 10),
        strip.text = element_text(size = 16),
        plot.title = element_text(size = 20, 
                                  face = "bold"))

plot_box

# saving plot 
ggsave(plot = plot_box,
       filename = "Plots/plot_box.svg",
       height = 5,
       width = 8,
       units = "in")

@@

```{r}
df_steps <- read_rds(file = "data/steps.rds")
set.seed(5678)
ggplot(data = df_steps,
       mapping = aes(x = type,
                     y = Steps
                     )
       ) +
  geom_boxplot(mapping = aes(color = type),
               fill = "grey",
               alpha = 0.6) +
  geom_jitter(mapping = aes(color = type),
              alpha = 0.9,
              width = 0.3) +
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  labs(x = "",
       y = "Steps During\nMain Phase") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()
        )

### Validation of steps
# selecting some rows at random with sample_n()
sample_n(df_steps, 6)

# random ID Output:
# Novices ID: 102, 125, 110
# Experts ID: 219, 218, 214

# Results from manual step counting:
# Novices ID: 110 -> 178 steps; 102 -> 219 steps; 125 -> 319 steps
# Experts ID: 214 -> 437 steps; 218 -> 195 steps; 219 -> 530 steps
